Scheeper's Meager-NWD Game and the Menger Game

### 2014-04-30 phd/dissertation/chapter5.tex
Begun work on chapter 2

  \begin{definition}
    $X$ is \textbf{Menger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist finite subcollections $\mathcal{F}_n \subseteq \mathcal{U}_n$ such that $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{definition}

  \begin{proposition}
    $\sigma$-compact $\Rightarrow$ Menger $\Rightarrow$ Lindelof
  \end{proposition}

  \begin{definition}
    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$. $F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{definition}

  \begin{theorem}
    $X$ is Menger if and only if $C \not\win \mengame{X}$.
  \end{theorem}

@@

  \begin{proposition}
    $X$ is compact if and only if $F \tactwin \mengame{X}$ if and only if $F \ktactwin{k} \mengame{X}$
  \end{proposition}

@@

  \begin{proposition}
    If $X$ is $\sigma$-compact then $F \markwin \mengame{X}$
  \end{proposition}

@@

  \begin{theorem}
  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
  \end{theorem}

@@

  \begin{lemma}
    For all functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, there exists a sequence $\alpha_0, \alpha_1, \dots < \omega_1$ such that $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
  \end{lemma}

@@

  \begin{example}
    $F \win \mengame{\oneptlind{\omega_1}}$ but $F \not\markwin \mengame{\oneptlind{\omega_1}}$.
  \end{example}

@@

  \begin{definition}
    A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
  \end{definition}

  \begin{proposition}
    If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
  \end{proposition}

@@

  \begin{lemma}
    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
      \[
        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
  \end{lemma}

@@

  \begin{corollary}
    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
  \end{corollary}

  \begin{corollary}
    For regular spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \markwin \mengame{X}$
      \end{enumerate}
  \end{corollary}

  \begin{theorem}
    For second-countable $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \mengame{X}$
        \item $F\markwin \mengame{X}$
      \end{enumerate}
  \end{theorem}

@@

  \begin{corollary}
    For metric spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \mengame{X}$
        \item $F \markwin \mengame{X}$
      \end{enumerate}
  \end{corollary}

  \begin{example}
  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed. This space is a non-regular example where $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
  \end{example}

@@

  \begin{example}
  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed. This space is non-regular, and non-$\sigma$-compact, but is second-countable and $\sigma$-(relatively compact).
  \end{example}

@@

  \begin{definition}
    Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.

    We say $X$ is \scish~if there exist functions $r_{\mc V}:X\to\omega$ for each open cover $\mc V$ of $X$ such that both of the following sets are $\mc V$-compact for all open covers $\mc U$, $\mc V$ and $n<\omega$:
      \[
        c(\mc V,n)=\{ x\in X : r_{\mc V}(x)\leq n\}
      \]
      \[
        p(\mc U,\mc V)=\{ x\in X : 0<r_{\mc U}(x)<r_{\mc V}(x)\}
      \]
  \end{definition}

  \begin{definition}
    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$. If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\alcomp g$).
  \end{definition}

  \begin{lemma}\label{kunlem}
    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \alcomp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals. In addition, the range of each $f_\alpha$ is co-infinite.
  \end{lemma}

@@

  \begin{theorem}
    The one-point Lindel\"ofication of the uncountable discrete space, $\oneptlind{\omega_1}$, is \scish.
  \end{theorem}

@@

  \begin{theorem}
    If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
  \end{theorem}

@@

  \begin{corollary}
    $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
  \end{corollary}

  \begin{definition} 
    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
  \end{definition}

  \begin{proposition}
    $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
  \end{proposition}

@@

  \begin{theorem}
    $S(\kappa,\omega,\omega)$ implies $\oneptlind{\kappa}$ is \scish.
  \end{theorem}

@@

  \begin{corollary}
    $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$.
  \end{corollary}

  \begin{definition}
    A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$. Let the set of all finite partial functions from $A$ to $B$ be denoted by $Fn(A,B)$.

    Then let $Fn^2(\mc A,B)\subset Fn(\mc A,Fn(\bigcup \mc A,B))$ such that for each $p\in Fn^2(\mc A,B)$, $p(A)=p_A\in Fn(A,B)$.
  \end{definition}

  \begin{definition}
    Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
          \begin{itemize}
            \item $\dom(q)\supseteq\dom(p)$
            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, for $\alpha\in A\cap B$ 
              \[
                \alpha\in\dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
                \Rightarrow
                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
              \]
          \end{itemize}
  \end{definition}

  \begin{lemma}
    $\pok$ has property $K$ (and thus is c.c.c.). That is, let $P\subseteq\pok$ be uncountable: there is an uncountable $Q\subseteq P$ such that points in $Q$ are pairwise compatible.
  \end{lemma}

@@

  \begin{proposition}
    For $A\in[\kappa]^\omega$ and $\alpha\in A$, the sets 
      \[
        D_A = \{p\in\pok: A\in\dom(p)\}
      \]
      \[
        D_{A,\alpha} = \{p\in\pok: A\in\dom(p), \alpha\in\dom(p_A)\}
      \]
    are dense in $\pok$.
  \end{proposition}

@@

  \begin{theorem}
    $S(\kappa,\omega,\omega)+(\kappa=2^\omega)$ is consistent with ZFC for any cardinal $\kappa$ with $cf(\kappa)>\omega$.
  \end{theorem}

@@

  \begin{corollary}
    For each $\kappa$, $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
  \end{corollary}

@@

  \begin{definition}
    A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
  \end{definition}

  \begin{proposition}
    Every ample cover of a regular space $X$ is really ample.
  \end{proposition}

@@

  \begin{definition}
    A space $X$ is (\textbf{relatively}) \textbf{Alster} if there exists a countable subcover for each (really) ample cover of $X$ by $G_\delta$ sets.
  \end{definition}

  \begin{proposition}
    Every regular relatively Alster space is Alster.
  \end{proposition}

  \begin{theorem}
    $X$ $\sigma$-compact $\Rightarrow$ $X$ Alster $\Rightarrow$ $X$ Menger
  \end{theorem}

@@

  \begin{proposition}
    $X$ $\sigma$-(relatively compact) $\Rightarrow$ $X$ relatively Alster $\Rightarrow$ $X$ Menger
  \end{proposition}

@@

  \begin{example}
    Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed. $R$ is not relatively Alster and $F\win\mengame{R}$. If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\mengame{R}$.
  \end{example}

@@

  \begin{definition}
    A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
  \end{definition}

@@

  \begin{definition}
    The \textbf{filling game} $\fillgame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$. In round $n+1$, player $M$ chooses $M_{n+1}$ where $M_n\subseteq M_{n+1}\in\<J\>$, and player $N$ replies with $N_{n+1}\in J$. Player $N$ wins the game if $\bigcup_{n<\omega} N_n \supseteq \bigcup_{n<\omega} M_n$. (The sets in $J$ and $\<J\>$ are thought of as nowhere-dense and meager sets, respectively.)

    The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$. This game has been studied by Scheepers.
  \end{definition}

  \begin{theorem}
    $N\ktactwin{2}\sfillgame{J} \Rightarrow N\kmarkwin{2}\fillgame{J}$
  \end{theorem}

@@

  \begin{example}
    There is a free ideal $J$ such that $N\not\ktactwin{2}\sfillgame{J}$ but $N\kmarkwin{2}\fillgame{J}$.
  \end{example}

@@

  \begin{definition}
    $X$ is \textbf{Rothberger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist open sets $U_n\in \mathcal{U}_n$ such that $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{definition}

  \begin{proposition}
    Rothberger $\Rightarrow$ Menger
  \end{proposition}

  \begin{definition}
    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing an open set $U_n\in\mathcal{U}_n$. $S$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{definition}

  \begin{theorem}
    $X$ is Rothberger if and only if $C\not\win\rothgame{X}$.
  \end{theorem}

@@

  \begin{definition}
    A space $X$ is scattered if every subspace contains an isolated point. By convention, $\ds X = \bigcup_{\alpha<\rank(X)}X^\alpha$ where $X^\alpha$ is the set of isolated points of $\ds X\setminus\bigcup_{\beta<\alpha}X^\beta$.
  \end{definition}

  \begin{proposition}
    A space $X$ is scattered if and only if every closed subspace contains an isolated point.
  \end{proposition}

  \begin{proposition}
    The rank of a compact scattered $T_1$ space is a successor ordinal, and $X^{\rank(X)-1}$ is finite.
  \end{proposition}

@@

  \begin{theorem}
    The following are equivalent for compact $T_2$ $X$:
      \begin{enumerate}[(a)]
        \item $X$ is Rothberger
        \item $X$ is scattered
        \item $S\win\rothgame{X}$
        \item $C\not\win\rothgame{X}$
      \end{enumerate}
  \end{theorem}

@@

  \begin{definition}
    In the two-player game $\altrothgame{X}$ player $P$ chooses points $x_n\in X$, followed by player $O$ choosing an open neighborhood $U_n$ of $x_n$. $P$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{definition}

  \begin{theorem} $\altrothgame{X}$ is ``perfect information equivalent'' to $\rothgame{X}$. That is:

    \begin{itemize}
      \item $P\win\altrothgame{X}$ if and only if $S\win\rothgame{X}$
      \item $O\win\altrothgame{X}$ if and only if $C\win\rothgame{X}$.
    \end{itemize}
  \end{theorem}

@@

  \begin{theorem}
    \begin{itemize}
      \item $P\prewin\altrothgame{X}$ if and only if $S\markwin\rothgame{X}$
      \item $O\markwin\altrothgame{X}$ if and only if $C\prewin\rothgame{X}$.
    \end{itemize}
  \end{theorem}

@@

  \begin{definition}
    Let $\mc{N}(x)$ be the $\textbf{neighborhood network}$ of $x$, that is, the collection of all neighborhoods of $x$.
  \end{definition}

  \begin{definition}
    A topological space $X$ is \textbf{almost countable} if there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$.
  \end{definition}

  \begin{theorem}
    For any space $X$, the following are equivalent:
    \begin{itemize}
      \item $S\markwin\rothgame{X}$ 
      \item $P\prewin\altrothgame{X}$
      \item $X$ is almost countable
    \end{itemize}
  \end{theorem}

@@

  \begin{theorem}
    For any $T_1$ space $X$, the following are equivalent:
    \begin{itemize}
      \item $S\markwin\rothgame{X}$
      \item $P\prewin\altrothgame{X}$
      \item $X$ is almost countable
      \item $|X|\leq\omega$
    \end{itemize}
  \end{theorem}

@@

  \begin{example}
    Let $X=\omega_1\cup\{\infty\}$ be a ``weak Lindel\"ofication'' of discrete $\omega_1$ such that open neighborhoods of $\infty$ contain $\omega_1\setminus\omega$. This space is $T_0$ but not $T_1$, and note that $S\markwin\rothgame{X}$ and $|X|>\omega$.
  \end{example}

  \begin{theorem}
    The following are equivalent for points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $S\win\rothgame{X}$
        \item $P\win\altrothgame{X}$
        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
        \item $P\kmarkwin{k}\altrothgame{X}$ for some $k\geq 1$
        \item $S\markwin\rothgame{X}$
        \item $P\prewin\altrothgame{X}$
        \item $X$ is almost countable
        \item $|X|\leq\omega$
      \end{enumerate}
  \end{theorem}

@@

  \begin{corollary}
    The following are equivalent for compact points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $S\win\rothgame{X}$
        \item $P\win\altrothgame{X}$
        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
        \item $P\kmarkwin{k}\altrothgame{X}$ for some $k\geq 1$
        \item $S\markwin\rothgame{X}$
        \item $P\prewin\altrothgame{X}$
        \item $X$ is almost countable
        \item $|X|\leq\omega$
        \item $C\not\win\rothgame{X}$
        \item $O\not\win\altrothgame{X}$
        \item $X$ is Rothberger
        \item $X$ is scattered
      \end{enumerate}
  \end{corollary}

>>>>

  \begin{defn}
    $X$ is \textbf{Menger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist finite subcollections $\mathcal{F}_n \subseteq \mathcal{U}_n$ such that $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{defn}

  \begin{prop}
    $\sigma$-compact $\Rightarrow$ Menger $\Rightarrow$ Lindelof
  \end{prop}

  \begin{defn}
    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$. $F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{defn}

  \begin{thm}
    $X$ is Menger if and only if $C \not\win \mengame{X}$.
  \end{thm}

@@

  \begin{prop}
    $X$ is compact if and only if $F \tactwin \mengame{X}$ if and only if $F \ktactwin{k} \mengame{X}$
  \end{prop}

@@

  \begin{prop}
    If $X$ is $\sigma$-compact then $F \markwin \mengame{X}$
  \end{prop}

@@

  \begin{thm}
  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
  \end{thm}

@@

  \begin{lem}
    For all functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, there exists a sequence $\alpha_0, \alpha_1, \dots < \omega_1$ such that $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
  \end{lem}

@@

  \begin{ex}
    $F \win \mengame{\oneptlind{\omega_1}}$ but $F \not\markwin \mengame{\oneptlind{\omega_1}}$.
  \end{ex}

@@

  \begin{defn}
    A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
  \end{defn}

  \begin{prop}
    If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
  \end{prop}

@@

  \begin{lem}
    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
      \[
        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
  \end{lem}

@@

  \begin{cor}
    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
  \end{cor}

  \begin{cor}
    For regular spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \markwin \mengame{X}$
      \end{enumerate}
  \end{cor}

  \begin{thm}
    For second-countable $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \mengame{X}$
        \item $F\markwin \mengame{X}$
      \end{enumerate}
  \end{thm}

@@

  \begin{cor}
    For metric spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \mengame{X}$
        \item $F \markwin \mengame{X}$
      \end{enumerate}
  \end{cor}

  \begin{ex}
  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed. This space is a non-regular example where $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
  \end{ex}

@@

  \begin{ex}
  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed. This space is non-regular, and non-$\sigma$-compact, but is second-countable and $\sigma$-(relatively compact).
  \end{ex}

@@

  \begin{defn}
    Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.

    We say $X$ is \scish~if there exist functions $r_{\mc V}:X\to\omega$ for each open cover $\mc V$ of $X$ such that both of the following sets are $\mc V$-compact for all open covers $\mc U$, $\mc V$ and $n<\omega$:
      \[
        c(\mc V,n)=\{ x\in X : r_{\mc V}(x)\leq n\}
      \]
      \[
        p(\mc U,\mc V)=\{ x\in X : 0<r_{\mc U}(x)<r_{\mc V}(x)\}
      \]
  \end{defn}

  \begin{defn}
    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$. If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\alcomp g$).
  \end{defn}

  \begin{lem}\label{kunlem}
    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \alcomp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals. In addition, the range of each $f_\alpha$ is co-infinite.
  \end{lem}

@@

  \begin{thm}
    The one-point Lindel\"ofication of the uncountable discrete space, $\oneptlind{\omega_1}$, is \scish.
  \end{thm}

@@

  \begin{thm}
    If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
  \end{thm}

@@

  \begin{cor}
    $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
  \end{cor}

  \begin{defn} 
    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
  \end{defn}

  \begin{prop}
    $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
  \end{prop}

@@

  \begin{thm}
    $S(\kappa,\omega,\omega)$ implies $\oneptlind{\kappa}$ is \scish.
  \end{thm}

@@

  \begin{cor}
    $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$.
  \end{cor}

  \begin{defn}
    A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$. Let the set of all finite partial functions from $A$ to $B$ be denoted by $Fn(A,B)$.

    Then let $Fn^2(\mc A,B)\subset Fn(\mc A,Fn(\bigcup \mc A,B))$ such that for each $p\in Fn^2(\mc A,B)$, $p(A)=p_A\in Fn(A,B)$.
  \end{defn}

  \begin{defn}
    Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
          \begin{itemize}
            \item $\dom(q)\supseteq\dom(p)$
            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, for $\alpha\in A\cap B$ 
              \[
                \alpha\in\dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
                \Rightarrow
                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
              \]
          \end{itemize}
  \end{defn}

  \begin{lem}
    $\pok$ has property $K$ (and thus is c.c.c.). That is, let $P\subseteq\pok$ be uncountable: there is an uncountable $Q\subseteq P$ such that points in $Q$ are pairwise compatible.
  \end{lem}

@@

  \begin{prop}
    For $A\in[\kappa]^\omega$ and $\alpha\in A$, the sets 
      \[
        D_A = \{p\in\pok: A\in\dom(p)\}
      \]
      \[
        D_{A,\alpha} = \{p\in\pok: A\in\dom(p), \alpha\in\dom(p_A)\}
      \]
    are dense in $\pok$.
  \end{prop}

@@

  \begin{thm}
    $S(\kappa,\omega,\omega)+(\kappa=2^\omega)$ is consistent with ZFC for any cardinal $\kappa$ with $cf(\kappa)>\omega$.
  \end{thm}

@@

  \begin{cor}
    For each $\kappa$, $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
  \end{cor}

@@

  \begin{defn}
    A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
  \end{defn}

  \begin{prop}
    Every ample cover of a regular space $X$ is really ample.
  \end{prop}

@@

  \begin{defn}
    A space $X$ is (\textbf{relatively}) \textbf{Alster} if there exists a countable subcover for each (really) ample cover of $X$ by $G_\delta$ sets.
  \end{defn}

  \begin{prop}
    Every regular relatively Alster space is Alster.
  \end{prop}

  \begin{thm}
    $X$ $\sigma$-compact $\Rightarrow$ $X$ Alster $\Rightarrow$ $X$ Menger
  \end{thm}

@@

  \begin{prop}
    $X$ $\sigma$-(relatively compact) $\Rightarrow$ $X$ relatively Alster $\Rightarrow$ $X$ Menger
  \end{prop}

@@

  \begin{ex}
    Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed. $R$ is not relatively Alster and $F\win\mengame{R}$. If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\mengame{R}$.
  \end{ex}

@@

  \begin{defn}
    A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
  \end{defn}

@@

  \begin{defn}
    The \textbf{filling game} $\fillgame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$. In round $n+1$, player $M$ chooses $M_{n+1}$ where $M_n\subseteq M_{n+1}\in\<J\>$, and player $N$ replies with $N_{n+1}\in J$. Player $N$ wins the game if $\bigcup_{n<\omega} N_n \supseteq \bigcup_{n<\omega} M_n$. (The sets in $J$ and $\<J\>$ are thought of as nowhere-dense and meager sets, respectively.)

    The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$. This game has been studied by Scheepers.
  \end{defn}

  \begin{thm}
    $N\ktactwin{2}\sfillgame{J} \Rightarrow N\kmarkwin{2}\fillgame{J}$
  \end{thm}

@@

  \begin{ex}
    There is a free ideal $J$ such that $N\not\ktactwin{2}\sfillgame{J}$ but $N\kmarkwin{2}\fillgame{J}$.
  \end{ex}

@@

  \begin{defn}
    $X$ is \textbf{Rothberger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist open sets $U_n\in \mathcal{U}_n$ such that $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{defn}

  \begin{prop}
    Rothberger $\Rightarrow$ Menger
  \end{prop}

  \begin{defn}
    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing an open set $U_n\in\mathcal{U}_n$. $S$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{defn}

  \begin{thm}
    $X$ is Rothberger if and only if $C\not\win\rothgame{X}$.
  \end{thm}

@@

  \begin{defn}
    A space $X$ is scattered if every subspace contains an isolated point. By convention, $\ds X = \bigcup_{\alpha<\rank(X)}X^\alpha$ where $X^\alpha$ is the set of isolated points of $\ds X\setminus\bigcup_{\beta<\alpha}X^\beta$.
  \end{defn}

  \begin{prop}
    A space $X$ is scattered if and only if every closed subspace contains an isolated point.
  \end{prop}

  \begin{prop}
    The rank of a compact scattered $T_1$ space is a successor ordinal, and $X^{\rank(X)-1}$ is finite.
  \end{prop}

@@

  \begin{thm}
    The following are equivalent for compact $T_2$ $X$:
      \begin{enumerate}[(a)]
        \item $X$ is Rothberger
        \item $X$ is scattered
        \item $S\win\rothgame{X}$
        \item $C\not\win\rothgame{X}$
      \end{enumerate}
  \end{thm}

@@

  \begin{defn}
    In the two-player game $\altrothgame{X}$ player $P$ chooses points $x_n\in X$, followed by player $O$ choosing an open neighborhood $U_n$ of $x_n$. $P$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{defn}

  \begin{thm} $\altrothgame{X}$ is ``perfect information equivalent'' to $\rothgame{X}$. That is:

    \begin{itemize}
      \item $P\win\altrothgame{X}$ if and only if $S\win\rothgame{X}$
      \item $O\win\altrothgame{X}$ if and only if $C\win\rothgame{X}$.
    \end{itemize}
  \end{thm}

@@

  \begin{thm}
    \begin{itemize}
      \item $P\prewin\altrothgame{X}$ if and only if $S\markwin\rothgame{X}$
      \item $O\markwin\altrothgame{X}$ if and only if $C\prewin\rothgame{X}$.
    \end{itemize}
  \end{thm}

@@

  \begin{defn}
    Let $\mc{N}(x)$ be the $\textbf{neighborhood network}$ of $x$, that is, the collection of all neighborhoods of $x$.
  \end{defn}

  \begin{defn}
    A topological space $X$ is \textbf{almost countable} if there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$.
  \end{defn}

  \begin{thm}
    For any space $X$, the following are equivalent:
    \begin{itemize}
      \item $S\markwin\rothgame{X}$ 
      \item $P\prewin\altrothgame{X}$
      \item $X$ is almost countable
    \end{itemize}
  \end{thm}

@@

  \begin{thm}
    For any $T_1$ space $X$, the following are equivalent:
    \begin{itemize}
      \item $S\markwin\rothgame{X}$
      \item $P\prewin\altrothgame{X}$
      \item $X$ is almost countable
      \item $|X|\leq\omega$
    \end{itemize}
  \end{thm}

@@

  \begin{ex}
    Let $X=\omega_1\cup\{\infty\}$ be a ``weak Lindel\"ofication'' of discrete $\omega_1$ such that open neighborhoods of $\infty$ contain $\omega_1\setminus\omega$. This space is $T_0$ but not $T_1$, and note that $S\markwin\rothgame{X}$ and $|X|>\omega$.
  \end{ex}

  \begin{thm}
    The following are equivalent for points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $S\win\rothgame{X}$
        \item $P\win\altrothgame{X}$
        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
        \item $P\kmarkwin{k}\altrothgame{X}$ for some $k\geq 1$
        \item $S\markwin\rothgame{X}$
        \item $P\prewin\altrothgame{X}$
        \item $X$ is almost countable
        \item $|X|\leq\omega$
      \end{enumerate}
  \end{thm}

@@

  \begin{cor}
    The following are equivalent for compact points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $S\win\rothgame{X}$
        \item $P\win\altrothgame{X}$
        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
        \item $P\kmarkwin{k}\altrothgame{X}$ for some $k\geq 1$
        \item $S\markwin\rothgame{X}$
        \item $P\prewin\altrothgame{X}$
        \item $X$ is almost countable
        \item $|X|\leq\omega$
        \item $C\not\win\rothgame{X}$
        \item $O\not\win\altrothgame{X}$
        \item $X$ is Rothberger
        \item $X$ is scattered
      \end{enumerate}
  \end{cor}

  \begin{defn}
    The game $\recallgame{m}{\kappa}$ proceeds as follows: during round $0$, player $F$ chooses $F_0\in[\kappa]^m$, followed by player $S$ choosing $x_0\in F_0\cup\{\infty\}$. During round $n+1$, $F$ chooses $F_{n+1}\in[\kappa]^{m^{n+2}}$ such that $F_{n+1}\supset F_n$, followed by $S$ choosing $x_{n+1}\in F_{n+1}\cup\{\infty\}$.

    $S$ wins the game if $\{x_n : n<\omega\}\supseteq F_0\cup\{\infty\}$, and $F$ wins otherwise.
  \end{defn}
